---
output:
  knitrBootstrap::bootstrap_document:
    theme.chooser: TRUE
    highlight.chooser: TRUE
  html_document:
    toc: true
    theme: united
---

Women doing data stuff on Twitter
=================================

```{r bibsetup, echo=FALSE, message=FALSE, warning=FALSE}
## Load knitcitations with a clean bibliography
library('knitcitations')
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')

bibs <- c('knitcitations' = citation('knitcitations'),
    'knitr' = citation('knitr')[1]
)
write.bibtex(bibs, file = 'NewPostRefs.bib')
bib <- read.bibtex('NewPostRefs.bib')
names(bib) <- names(bibs)
```

A list of women doing great data things on Twitter 
(started at [_A non-comprehensive list of awesome female data people on Twitter_](http://simplystatistics.org/2014/09/09/a-non-comprehensive-list-of-awesome-female-data-people-on-twitter/))


I was just talking to a student who mentioned she didn't know Jenny Bryan was on Twitter. She is and she is an awesome person to follow. I also realized that I hadn't seen a good list of women on Twitter who do stats/data. So I thought I'd make one. This list is what I could make in 15 minutes based on my own feed and will, with 100% certainty, miss really good people. Can you please add them in the comments and I'll update the list?

```{r 'input', bootstrap.show.code = FALSE}
## Input data
womenTwitter <- data.frame(
    Handle = c(
        '@JennyBryan',
        '@hspter',
        '@acfrazee',
        '@emsweene57',
        '@hmason',
        '@sherrirose',
        '@eloyan_ani',
        '@mrogati',
        '@annmariastat',
        '@kara_woo',
        '@jhubiostat',
        '@lovestats',
        '@ProfEmilyOster',
        '@monachalabi',
        '@lisaczhang',
        '@notawful',
        '@AliciaOshlack',
        '@AmeliaMN',
        '@leighadlr',
        '@inesgn',
        '@sgrifter',
        '@ladamic',
        '@stephaniehicks',
        '@ansate',
        '@lauramclay',
        '@bioannie',
        '@kaythaney',
        '@laurieskelly',
        '@bo_p',
        '@siminaboca',
        '@HelenPowell01',
        '@victoriastodden'
    ),
    Name = c(
        'Jenny Bryan',
        'Hilary Parker',
        'Alyssa Frazee',
        'Elizabeth Sweeney',
        'Hilary Mason',
        'Sherri Rose',
        'Ani Eloyan',
        'Monica Rogati',
        'AnnMaria De Mars',
        'Kara Woo',
        'Betsy Ogburn',
        'Annie Pettit',
        'Emily Oster',
        'Mona Chalabi',
        'Lisa Zhang',
        'Jessica Hartnett',
        'Alicia Oshlack',
        'Amelia McNamara',
        'LEIGH ARINO DE LA RUBIA',
        'Ines Germendia',
        'Sandy Griffith',
        'Lada Adamic',
        'Stephanie Hicks',
        'Melissa Santos',
        'Laura McClay',
        'Laura Hatfield',
        'Kaitlin Thaney',
        'Laurie Skelly',
        'Bo Peng',
        'Simina Boca',
        'Helen Powell',
        'Victoria Stodden'
    ),
    Description = c(
        'statistics professor at UBC, teaching a great intro to data science class right now',
        'data analyst at Etsy (former Hopkins grad student!) and co-creator (I think) of #rcatladies, also wrote this nice post on writing an R package from scratch',
        'Ph.D. student at Hopkins, writes a great blog on data stuff, works on statistical genomics',
        'Hopkins Ph.D. student, developer of methods for neuroimaging',
        'currently running one of my favorite startups Fast Forward Labs, but basically needs no introduction, one of the biggest names in data science right now',
        'former Hopkins postdoc, now at Harvard. Literally wrote the book on targeted learning',
        'Hopkins Biostat faculty, working on neuroimaging and EMRs. Lead the team that won the ADHD-200 competition',
        'Former Linkedin data scientist, now running the data team at Jawbone',
        'runs the Julia group, also world class judoka, writes one of my favorite stats/education blogs',
        'Works at the National Center for Ecological Analysis and Synthesis and maintains their projections blog',
        'Hopkins biostat faculty, not technically her account. But she is the reason this is the funniest/best academic department twitter account out there',
        'Does surveys and data quality/MRX work. If you are into MRX, check out her blog',
        'Econ professor at U Chicago. Has been my favorite writer for FiveThirtyEight since their relaunch',
        'writer for FiveThirtyEight, I like her "Am I normal" series of posts',
        'cofounder of Polychart',
        'professor at Gannon University, writes a great blog on teaching statistics',
        "researcher at Murdoch Children's research institute, one of the real superstars in computational genomics",
        'graduate student at UCLA, works on the Mobilize project and other awesome data education initiatives in LA school system',
        'Editor in chief of DataScience.LA',
        'data scientist working on official statistics at Basque Statistics - Eustat',
        'Biostat Ph.D., fellow #rcatladies creator, professor at the Cleveland Clinic in quantitative medicine',
        'professor at Michigan, teacher of really highly regarded social network analysis class on Coursera, now at Facebook (I think)',
        'postdoc in compbio at Harvard, lead teaching assistant for Data Science course at Harvard',
        'manager of Hadoop infrastructure at Etsy, maintainer of the women in data list below',
        'professor of operations research at UW Madison, writes a blog with an amazing name: Punk Rock Operations Research',
        "professor at Harvard, also has one of the best data titles I've ever heard: Princess of Bayesia",
        'director of the Mozilla Science Lab, also works with Data Kind UK',
        'Data scientist at Data Scope analytics',
        'Data scientist at Data Scope analytics',
        'former Hopkins Ph.D. student, now assistant professor at Georgetown in Biomedical informatics',
        'postdoc in Biostatistics at Hopkins, works on statistics for relationship between air pollution and health',
        'one of the leaders in the legal and sociological aspects of reproducible research'
    )
)
## Add links to follow
womenTwitter$Follow <- paste0("<a href=\"https://twitter.com/",
    gsub('@', '', womenTwitter$Handle),
    "\" class=\"twitter-follow-button\" data-show-count=\"false\">",
    womenTwitter$Handle, "</a>")
```




<link rel='stylesheet' href='http://ajax.aspnetcdn.com/ajax/jquery.dataTables/1.9.4/css/jquery.dataTables.css' />
<script src='http://ajax.aspnetcdn.com/ajax/jquery.dataTables/1.9.4/jquery.dataTables.min.js'></script>

<script>!function(d,s,id){var js,fjs=d.getElementsByTagName(s)[0],p=/^http:/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document, 'script', 'twitter-wjs');</script>

```{r, results = 'asis', echo = FALSE}
library('knitr')
## Display the data
kable(womenTwitter[, c('Follow', 'Name', 'Description')], format = 'html', table.attr='id="women_twitter"')
```


<script type="text/javascript" charset="utf-8">
$(document).ready(function() {
    $('#women_twitter').dataTable({
        "sPaginationType": "full_numbers",
        "sScrollX": "100%",
        "iDisplayLength": 10
    });
});
</script>


Interactive table powered by [DataTables](http://www.datatables.net/) and `knitr` `r citep(bib[['knitr']])`.


# More

I have also been informed that these Twitter lists are probably better than my post. But I'll keep updating my list anyway cause I want to know who all the right people to follow are!

* [women-in-data](https://twitter.com/ansate/lists/women-in-data)
* [women-in-data-science](https://twitter.com/BecomingDataSci/lists/women-in-data-science)

# References

Citations made with `knitcitations` `r citep(bib[['knitcitations']])`.


```{r bibliography, results='asis', echo=FALSE, cache=FALSE}
## Print bibliography
bibliography()
```


```{r 'cleanupBib', echo = FALSE, results = 'hide'}
## Clean up
file.remove('NewPostRefs.bib')
```

Date this page was last rendered:

```{r date, echo = FALSE}
## date
Sys.time()
```

